\newpage
\addcontentsline{toc}{section}{Appendices}
\begin{appendices}
    %\appendixpage
    \section{Digital ressources}
    Attached to the thesis is a data medium that holds all cited sources, developed and used source code, graphics and
    analyses using e.g.\ Jupyter Notebooks. Below is an overview of each folder present on the disk with a short description
    of its contents.

    \begin{description}
        \item[README.html] is a document holding information about the additional information contained on the DVD as well
            as links to further information
        \item[analysis] Holds all Jupyter Notebooks. See them also directly on
            \url{https://github.com/pascalwhoop/broker-python/tree/master/notebooks}.
        \item[code\_and\_data] contains a 2.4GB zip file that contains all source code used and developed. It's a collection of \ac{PowerTAC}
            project folders as well as my own projects. It's a direct zip of my file system and therefore contains \texttt{.git}
            directories and links to the upstream GitHub repositories. It also contains all data used to train the demand predictor
            and the wholesale agent offline. This zip expands to over 16GB.
        \item[graphics] contains a number of generated graphics that was used to better understand competitor agents, the
            overall dynamics of the game and other information that can be best grasped when visualized.
        \item[sources] contains all papers, books and websites that were used to write the thesis
        \item[thesis] contains all sources and the rendered \text{main.pdf} file of the main thesis document
        \item[others] contains anything that didn't match the aforementioned categories
    \end{description}
\end{appendices}
