\section*{Preface}

This thesis was planned and discussed in the winter of 17/18. On February 1st, the work phase of six months started.
Within these six months, I discovered many previously unknown or unforeseen complexities. These include the
communication technologies developed to permit a complete python based broker and a large variety of API approaches
within the RL agent libraries currently available. While I have invested a significant amount of effort into the
development of the required components, I always intended to build something that may be reused in the future instead of
being discarded after my thesis was graded. This lead me to the decision of implementing a best practice based
communication instead of a quick minimal approach and led me to try and write my python code in a way that will let
future broker developers reuse it as a framework for their broker implementations. 

Why not just write another broker in Java? I believe PowerTAC answers an important question of our time. But I also
believe there are not enough people working on this field and it doesn't receive the attention it should. Thousands of
researchers and those who want to become one are working on getting AI agents to become better at Atari games or playing
Doom. While the underlying technology advancements are fantastic, the application area is of no use to humanity. I
wanted to apply these new technologies to a problem that matters and do so in a way that will create artifacts that
others can build upon to outperform my solutions quickly. I wanted to create a bridge between the researchers of RL
implementations of recent years and their large community and the exciting field of energy markets. PowerTAC offers
another "game" to play with, another environment to let agents compete in. But it is an environment which actually
generates value when explored.

As of July, I was not able to complete my research question and reach the intended target of evaluating a variety of
neural network architectures that let a RL learn from other agents in its environment. Because of university
regulations, changing a thesis title is not permitted. And while my research question was not answered, I believe I
still contributed something valuable to the PowerTAC community. With my implementation, current state-of-the-art neural
network algorithms and especially reinforcement agent implementations can be used to act in the PowerTAC competition.
Python developers can come and join the competition.
And while I was not able to create a well performing broker in time and compete with the current participants of the
competition, it is nonetheless now possible for others to work on a broker that deploys \ac{NN} technologies and to focus on the core problems of RL learning
problems: Environment observation filtering, NN input preprocessing, reward function definition, NN architecture
experimentation etc. With the created Docker images, developers are quickly able to start a competition with multiple
brokers and future participants may be encouraged to adopt the Docker based distribution of their agents to include more
advanced technologies in their broker implementations without placing a burden on others to manage these dependencies.
The new communication layer may be adopted by the competition maintainers to improve performance and to enable other
platforms to be used for writing brokers.   

When reading the thesis, please be aware that the title does not match the contents as one would expect. Adding a simple
"Towards" at the beginning of the title would make it a perfect fit again. Unfortunately, I fell into the same trap that
many software engineers and entire project teams fall into: Underestimating the complexity of the project which leads to
either loss in quality, time overruns or budget overruns. I chose quality of the work I completed over making it work
once but being useless for anyone else afterwards. I hope the thesis is still valuable to anyone who reads it and maybe
upcoming graduate theses will continue where I left off. 
